Experimental and numerical studies of the effects of resonant and random excitations of the proton beam in the LHC, with applications to the design of a pulsed hollow electron lens for active halo control

### 2018-03-02 resex.tex
Revised results section on pattern dependence (VI A).

In the presence of only a resonant excitation, this modified
distribution is stable in simulations with a constant emittance. As we
will see later, an increase of the emittance with the applied
excitation amplitude is however observed experimentally not matching
the prediction by simulations. By adding a random noise component
representative for the natural noise present in the LHC, the constant
emittance is changed in simulations to an excitation amplitude
dependent emittance growth after an initial adjustment phase. In case
of random uniform noise, the excitation leads to constant emittance
growth without any initial adjustment phase. The interaction with the
natural noise source then only results in an underestimation of loss
rates and emittance growth as it is basically equivalent to the
application of random noise with an increased amplitude. In addition
to the experiments presented in this paper, the effect of a random
excitation was also studied in a separate experiment at the LHC for
the case of colliding beams
\cite{md1433_noise_top_energy,md_noise_bbLHC}.

>>>>

If only the resonant excitation is present, without noise, simulations
show that the modified distribution is stable, with constant
emittance. By adding a random noise component, representative of the
natural noise present in the LHC, one calculates, after the initial
adjustment phase, emittance-growth rates that increase with the
amplitude of the excitation. As discussed below, an increase of the
emittance-growth rates with the applied excitation amplitude is what
is observed experimentally.

In the case of random excitation, there is constant emittance growth,
without any initial adjustment phase. The interaction with the natural
noise sources in the machine results in increased losses and emittance
growth, as it is basically equivalent to the application of a random
excitation with an increased amplitude. In addition to the experiments
presented in this paper, the effect of a random excitation was also
studied in a separate experiment at the LHC for the case of colliding
beams~\cite{md1433_noise_top_energy, md_noise_bbLHC}.
